Dynamics of Anthropomorphism in Human-Robot Interaction

### 2014-06-24 paper.tex
my first commit from my mac system
i hope this works … i had to comment out the tikz figures because they
don't work here

\usepackage{graphicx}
\graphicspath{{figs/}}
\usepackage{tikz}
\usetikzlibrary{shapes}
\usetikzlibrary{svg.path}
%
\usepackage{amsmath} 
\usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
\usepackage{color, soul}
\usepackage{url}
\usepackage{multirow}
\usepackage{array}
\usepackage{fixltx2e}
\usepackage{textcomp}

@@

\begin{figure*}[htb]
\centering

\begin{tikzpicture}[scale=1.4]

% background shading
\path[fill=green!20] (0,0) rectangle (0.6,5.5);
\path[fill=blue!15] (0.6,0) rectangle (5.2,5.5);
\path[fill=orange!20] (5.2,0) rectangle (9.8,5.5);
\draw(0,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Initialization};
\draw(2.5,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Familiarization};
\draw(6.5,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Stabilization};
% horizontal axis
\draw[->] (0,0) -- (10,0) node[anchor=north] {$t$};
\draw(5,-0.1) node[anchor=north] {\scriptsize Duration of interaction};

% vertical axis
\draw[->] (0,0) -- (0,6) node[anchor=east] {};
\draw(-0.8,3) node[rotate=90,anchor=south] {\scriptsize Anthropomorphic effects};

\draw (-0.05, 3) -- (0.05, 3) node[anchor=east] {\ICA};
\draw (-0.05, 5) -- (0.05, 5) node[anchor=east] {\AntMax};

% vertical axis - end
\draw[->] (9.8,0) -- (9.8,2) node[anchor=east] {};
\draw (9.8, 0.8) node[anchor=west] {\SLA};

\draw[<-] (0.65,5) -- (0.8,5.2) node[anchor=east] {};
\draw (0.9,5.3) node[anchor=west] {\tiny \it novelty peak};

\draw[dashed] (0.6, 0) -- (0.6,5.1);
\draw (0.6,0) node[anchor=north] {$t_{max}$};

\draw[dotted] (0, 5) -- (6.2,5);
\draw[dotted] (0, 3) -- (6.2,3);
\draw[<->] (6.1,3) -- (6.1,5) node[sloped, above, midway] {$\Delta_{a}$};

\draw[<-] (1.7,4.4) -- (3.2,4.1) node[anchor=east] {};
\draw[<-] (2.85,2.6) -- (3.2,4.1) node[anchor=east] {};
\draw (3.2,4.1) node[anchor=west, align=center] {\tiny \it disruptive\\ \tiny
\it behaviors};
%%%%%
%% CURVES
%%%%
\begin{scope}[yscale=-1,shift={(-0.125,-0.4)}]

    \draw[ultra thick] svg[scale=1cm] "M 0.125,-2.5619582 c 0.0200733,-1.1573591
    0.33954391,-1.9982333 0.57940683,-2.0013597 0.13691605,0 0.25550329,0.052908
    0.37497897,0.1661788 0.119476,0.1130305 0.2396954,0.2786079
    0.37944,0.4790565 0.069872,0.099803 0.1021612,-0.2231749
    0.1792538,-0.2238964 0.099707,0 0.013454,0.4985362 0.3173383,0.9139831
    0.1911917,0.2612926 0.3444354,0.2578391 0.6711932,0.4894291
    0.2058265,0.1458798 0.1571532,0.9762306 0.2615031,0.9702183 0.097182,0
    0.083295,-0.3336208 0.4330446,-0.1199242 0.4306401,0.2631203
    0.216699,0.1355642 0.4296663,0.2647074 2.0858202,1.13836043
    4.34683,1.41300027 6.3741749,1.43753027";

    \draw[dashed] svg[scale=1cm] "M 0.125,-0.1952939 c 0.0553601,-3.1917862
    0.33954391,-4.3648976 0.57940683,-4.368024 0.13691605,0 0.25550329,0.052908
    0.37497897,0.1661788 m 2.6714393,2.7735737 C 4.7653984,-0.85050947
    6.5955093,0.35382293 10.125,0.4062498";

    \draw[dashed] svg[scale=1cm] "M 0.125,-3.6923825 C 0.1102888,-4.0297903
    0.46454391,-4.5601915 0.70440683,-4.5633179 M 3.7508251,-1.6235654 C
    4.9579368,-0.95548345 8.1358175,-0.82609971 10.125,-0.79459549";

\end{scope}

\end{tikzpicture}

\caption{The dynamics of anthropomorphism. We distinguish three main phases:
    \emph{initialization}, \emph{familiarization} and \emph{stabilization},
    preceded by a \emph{pre-interaction} phase. The pre-interaction phase
    is characterized through an \emph{initial capital of anthropomorphism} (ICA, noted \ICA).
    Once the interaction starts, the level of anthropomorphism increases due to
    the \emph{novelty effect}, and then decreases to reach a \emph{stabilized
    level of anthropomorphism} (SLA, noted \SLA). \ICA and \SLA may vary
    depending on the user (and his/her expectations), the robot and the context of interaction.  During the
    interaction, unpredicted behaviors of the robot (\emph{disruptive
    behaviors}) may lead to local increases or decreases of the level of
    anthropomorphic effects.}

\label{fig:dynamics}
\end{figure*}

@@

\begin{figure}[htb]
\centering
%\resizebox{\linewidth}{!}{
\begin{tikzpicture}
\baselineskip=8pt

\path[fill=gray!20] (0,0) rectangle (10.5,2);
\path[fill=gray!50] (0,2) rectangle (10.5,4);
\path[fill=gray!20] (0,4) rectangle (10.5,6);

\draw (-0.3,1) node[rotate=90] {Stage 1}
      (-0.3,3) node[rotate=90] {Stage 2}
      (-0.3,5) node[rotate=90] {Stage 3};

\draw[->] (0,0) -- (11,0) node[anchor=north] {$t$};
\draw[-|] (0,0) -- (0,6.5) node[anchor=east] {};
% Us
\draw[ultra thick, ->] (0,0) -- (1,2) -- (3,2) -- (4,4) -- (6,4) -- (7,6) --
(9.5,6);
\draw[ultra thick, dashed, ->] (3,2) -- (9.5,2);
\draw[ultra thick, dashed, ->] (6,4) -- (9.5,4);

\draw (11,1) node[align=left, anchor=west]{\scriptsize pre-cognitive\\\scriptsize anthropomorphism}; %label

\draw (11,3) node[align=left, anchor=west] {\scriptsize{projection of existing}\\\scriptsize{mental models}\\\scriptsize{\it (familiarity)}}; %label

\draw (11,5) node[align=left, anchor=west] {\scriptsize{adapted mental
model} \\ $\to$ \scriptsize{adapted interaction}\\\scriptsize{\it (anthropomorphic or not)}}; %label

\draw[dashed,->] (1,0.1) to[bend right] (2,1.9)  node at (4.5,1) {\tiny{\it observation (shape, motion, sound)}}; %label

\draw[dashed,->] (4,2.1) to[bend right] (5,3.9)  node[align=left] at (7.5,3) {\tiny \it observation (interactive behavior) \\ \tiny \it or short interaction}; %label

\draw[dashed,->] (7,4.1) to[bend right] (8,5.9)  node[align=left] at (9,5)
{\tiny \it contextualized\\ \tiny \it interaction}; %label

\end{tikzpicture}
%}
\caption{The three cognitive stages of anthropomorphism: Stage 1 is the instinctive,
sub-cognitive identification of living peers. {\it Empathy} is characteristic
of this stage. After longer observation or short, non-contextualized interaction
(typically, a lab environment), the user reaches Stage 2: the user projects a
mental model he/she is already familiar with onto the robot. After longer {\it
contextualized} interaction (typically, at home), the user enters Stage 3 of
anthropomorphism: the user composes a custom mental model of the robot,
based on experience. This leads to adapted interaction modalities, that may
still be anthropomorphic, or not.}
\label{fig:cognitivemodel}
\end{figure}

>>>>

\usepackage{graphicx}
\graphicspath{{figs/}}
%\usepackage{tikz}
%\usetikzlibrary{shapes}
%\usetikzlibrary{svg.path}
%
\usepackage{amsmath} 
\usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
\usepackage{color, soul}
\usepackage{url}
\usepackage{multirow}
\usepackage{array}
\usepackage{fixltx2e}
\usepackage{textcomp}

@@

%\begin{figure*}[htb]
%\centering
%
%
%\begin{tikzpicture}[scale=1.4]
%
%% background shading
%\path[fill=green!20] (0,0) rectangle (0.6,5.5);
%\path[fill=blue!15] (0.6,0) rectangle (5.2,5.5);
%\path[fill=orange!20] (5.2,0) rectangle (9.8,5.5);
%\draw(0,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Initialization};
%\draw(2.5,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Familiarization};
%\draw(6.5,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Stabilization};
%% horizontal axis
%\draw[->] (0,0) -- (10,0) node[anchor=north] {$t$};
%\draw(5,-0.1) node[anchor=north] {\scriptsize Duration of interaction};
%
%
%% vertical axis
%\draw[->] (0,0) -- (0,6) node[anchor=east] {};
%\draw(-0.8,3) node[rotate=90,anchor=south] {\scriptsize Anthropomorphic effects};
%
%\draw (-0.05, 3) -- (0.05, 3) node[anchor=east] {\ICA};
%\draw (-0.05, 5) -- (0.05, 5) node[anchor=east] {\AntMax};
%
%% vertical axis - end
%\draw[->] (9.8,0) -- (9.8,2) node[anchor=east] {};
%\draw (9.8, 0.8) node[anchor=west] {\SLA};
%
%
%\draw[<-] (0.65,5) -- (0.8,5.2) node[anchor=east] {};
%\draw (0.9,5.3) node[anchor=west] {\tiny \it novelty peak};
%
%\draw[dashed] (0.6, 0) -- (0.6,5.1);
%\draw (0.6,0) node[anchor=north] {$t_{max}$};
%
%\draw[dotted] (0, 5) -- (6.2,5);
%\draw[dotted] (0, 3) -- (6.2,3);
%\draw[<->] (6.1,3) -- (6.1,5) node[sloped, above, midway] {$\Delta_{a}$};
%
%\draw[<-] (1.7,4.4) -- (3.2,4.1) node[anchor=east] {};
%\draw[<-] (2.85,2.6) -- (3.2,4.1) node[anchor=east] {};
%\draw (3.2,4.1) node[anchor=west, align=center] {\tiny \it disruptive\\ \tiny
%\it behaviors};
%%%%%%
%%% CURVES
%%%%%
%\begin{scope}[yscale=-1,shift={(-0.125,-0.4)}]
%
%    \draw[ultra thick] svg[scale=1cm] "M 0.125,-2.5619582 c 0.0200733,-1.1573591
%    0.33954391,-1.9982333 0.57940683,-2.0013597 0.13691605,0 0.25550329,0.052908
%    0.37497897,0.1661788 0.119476,0.1130305 0.2396954,0.2786079
%    0.37944,0.4790565 0.069872,0.099803 0.1021612,-0.2231749
%    0.1792538,-0.2238964 0.099707,0 0.013454,0.4985362 0.3173383,0.9139831
%    0.1911917,0.2612926 0.3444354,0.2578391 0.6711932,0.4894291
%    0.2058265,0.1458798 0.1571532,0.9762306 0.2615031,0.9702183 0.097182,0
%    0.083295,-0.3336208 0.4330446,-0.1199242 0.4306401,0.2631203
%    0.216699,0.1355642 0.4296663,0.2647074 2.0858202,1.13836043
%    4.34683,1.41300027 6.3741749,1.43753027";
%
%    \draw[dashed] svg[scale=1cm] "M 0.125,-0.1952939 c 0.0553601,-3.1917862
%    0.33954391,-4.3648976 0.57940683,-4.368024 0.13691605,0 0.25550329,0.052908
%    0.37497897,0.1661788 m 2.6714393,2.7735737 C 4.7653984,-0.85050947
%    6.5955093,0.35382293 10.125,0.4062498";
%
%    \draw[dashed] svg[scale=1cm] "M 0.125,-3.6923825 C 0.1102888,-4.0297903
%    0.46454391,-4.5601915 0.70440683,-4.5633179 M 3.7508251,-1.6235654 C
%    4.9579368,-0.95548345 8.1358175,-0.82609971 10.125,-0.79459549";
%
%
%
%\end{scope}
%
%\end{tikzpicture}
%
%\caption{The dynamics of anthropomorphism. We distinguish three main phases:
%    \emph{initialization}, \emph{familiarization} and \emph{stabilization},
%    preceded by a \emph{pre-interaction} phase. The pre-interaction phase
%    is characterized through an \emph{initial capital of anthropomorphism} (ICA, noted \ICA).
%    Once the interaction starts, the level of anthropomorphism increases due to
%    the \emph{novelty effect}, and then decreases to reach a \emph{stabilized
%    level of anthropomorphism} (SLA, noted \SLA). \ICA and \SLA may vary
%    depending on the user (and his/her expectations), the robot and the context of interaction.  During the
%    interaction, unpredicted behaviors of the robot (\emph{disruptive
%    behaviors}) may lead to local increases or decreases of the level of
%    anthropomorphic effects.}
%
%\label{fig:dynamics}
%\end{figure*}

@@

%\begin{figure}[htb]
%\centering
%%\resizebox{\linewidth}{!}{
%\begin{tikzpicture}
%\baselineskip=8pt
%
%\path[fill=gray!20] (0,0) rectangle (10.5,2);
%\path[fill=gray!50] (0,2) rectangle (10.5,4);
%\path[fill=gray!20] (0,4) rectangle (10.5,6);
%
%\draw (-0.3,1) node[rotate=90] {Stage 1}
%      (-0.3,3) node[rotate=90] {Stage 2}
%      (-0.3,5) node[rotate=90] {Stage 3};
%
%\draw[->] (0,0) -- (11,0) node[anchor=north] {$t$};
%\draw[-|] (0,0) -- (0,6.5) node[anchor=east] {};
%% Us
%\draw[ultra thick, ->] (0,0) -- (1,2) -- (3,2) -- (4,4) -- (6,4) -- (7,6) --
%(9.5,6);
%\draw[ultra thick, dashed, ->] (3,2) -- (9.5,2);
%\draw[ultra thick, dashed, ->] (6,4) -- (9.5,4);
%
%\draw (11,1) node[align=left, anchor=west]{\scriptsize pre-cognitive\\\scriptsize anthropomorphism}; %label
%
%\draw (11,3) node[align=left, anchor=west] {\scriptsize{projection of existing}\\\scriptsize{mental models}\\\scriptsize{\it (familiarity)}}; %label
%
%\draw (11,5) node[align=left, anchor=west] {\scriptsize{adapted mental
%model} \\ $\to$ \scriptsize{adapted interaction}\\\scriptsize{\it (anthropomorphic or not)}}; %label
%
%
%\draw[dashed,->] (1,0.1) to[bend right] (2,1.9)  node at (4.5,1) {\tiny{\it observation (shape, motion, sound)}}; %label
%
%\draw[dashed,->] (4,2.1) to[bend right] (5,3.9)  node[align=left] at (7.5,3) {\tiny \it observation (interactive behavior) \\ \tiny \it or short interaction}; %label
%
%\draw[dashed,->] (7,4.1) to[bend right] (8,5.9)  node[align=left] at (9,5)
%{\tiny \it contextualized\\ \tiny \it interaction}; %label
%
%\end{tikzpicture}
%%}
%\caption{The three cognitive stages of anthropomorphism: Stage 1 is the instinctive,
%sub-cognitive identification of living peers. {\it Empathy} is characteristic
%of this stage. After longer observation or short, non-contextualized interaction
%(typically, a lab environment), the user reaches Stage 2: the user projects a
%mental model he/she is already familiar with onto the robot. After longer {\it
%contextualized} interaction (typically, at home), the user enters Stage 3 of
%anthropomorphism: the user composes a custom mental model of the robot,
%based on experience. This leads to adapted interaction modalities, that may
%still be anthropomorphic, or not.}
%\label{fig:cognitivemodel}
%\end{figure}
